% Chapter Template

\chapter{Summary of the Research Plan} % Main chapter title

\label{Chapter4} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

In this proposal I have outlined a plan of original research to fulfill the dissertation requirements of the Ph.D. program in Biomedical Engineering.  Through the development and application of vibrational imaging, this work will elucidate several problems in biological physics.  The first two projects are roughly divided towards a pure science aim to investigate diffusion of cryoprotectants, and an applied science project in developing a sorting system based on signals derived from cellular metabolism.  The third project expressly extends the field of vibrational imaging by continuing on work that I've already started on the implementation of a new modality in the form of TSFG.  Characterizing that system will lead to immediate contributions to the field of biological imaging.

Based on the projects proposed here the format of my dissertation seems evident.  The first chapter shall examine the state of vibrational imaging with a focus on stimulated Raman scattering theory and application.  This chapter will be based in large part on the review article already published.  The second chapter will focus on the application of SRS and deuterium labeling to the characterization the new cell type known as lipochondrocytes.  As this work is soon to be sent for review, it will  not require much more effort to extend it to the level of a dissertation chapter.  Each of the three projects proposed here will be developed through the proposed investigations into a chapter each.  Additionally, as each of these projects is already begun in some preliminary form it is expected that they will each take a devoted amount of time of around six months.  This falls well into the schedule of my remaining program.  Completion of these projects within that time line would have me completing my dissertation around the end of the Summer 2020 term. This would be well withing the normal time to degree for students in the biomedical engineering program